### 2015-05-12 whoop.tex
updates in main section

\medskip\noindent\textbf{Semantics} Let $\ids$ be an infinite set from
which dynamic thread ids will be drawn.  The state of a running
concurrent program consists of: a valuation of the shared variables,
$\sharedvars$; a mapping that associates each mutex in $\mutexes$ with
an id from $\ids$, recording which thread currently holds the mutex,
or with a special value $\bot \notin \ids$ to indicate that the
mutex is not held by any thread; a list of \emph{threads}.  Each
thread consists of an id, drawn from $\ids$, a thread template, $T$,
an index indicating the next statement of the template $T$ to be
executed by the thread, and a valuation of the thread private
variables, $\variables{T}$.  If multiple threads are instances of the
same template $T$, then each thread carries a \emph{separate}
valuation of the private variables for this template.

@@

We consider a standard interleaving model of concurrency: at any
execution point, a thread may execute its current statement, unless
that statement has the form $\mutexlock{m}$ and mutex $m$ is already held
by some thread.  Executing a statement causes the state of the thread,
and the shared state, to be updated in a standard manner.  For
example, if a thread following template $T$ executes $s = e$, where $s
\in \sharedvars$ and $e$ is an expression over $\variables{T}$, the
shared variable valuation is updated so that $s$ has the value
determined by evaluating $e$ in the context of the thread's private
variable valuation.  The thread's next statement is updated according
to the control flow graph of the current procedure.

@@

\medskip\noindent\textbf{Lockset instrumentation }
Suppose that $S$ and $T$ are thread templates for a concurrent program, including the possibly that $S=T$.
We wish to check whether it is possible for a thread that is an instance of $S$ to race with a thread that is
an instance of $T$, in the presence of arbitrarily many further threads.

>>>>

\medskip\noindent\textbf{Semantics }
%
Let $\ids$ be an infinite set from which dynamic thread ids will be drawn.  The state of a running concurrent program consists of: a valuation of the shared variables, $\sharedvars$; a mapping that associates each mutex in $\mutexes$ with an id from $\ids$, recording which thread currently holds the mutex, or with a special value $\bot \notin \ids$ to indicate that the mutex is not held by any thread; and a list of \emph{threads}.  Each thread consists of an id, drawn from $\ids$, a thread template, $T$, an index indicating the next statement of $T$ to be executed by the thread, and a valuation of the thread private variables, $\variables{T}$.  If multiple threads are instances of the same template $T$, then each thread carries a \emph{separate} valuation of the private variables for this template.

@@

We consider a standard interleaving model of concurrency: at any execution point, a thread may execute its current statement, unless that statement has the form $\mutexlock{m}$ and mutex $m$ is already held by some thread.  Executing a statement causes the state of the thread, and the shared state, to be updated in a standard manner.  For example, if a thread following template $T$ executes $s = e$, where $s \in \sharedvars$ and $e$ is an expression over $\variables{T}$, the shared variable valuation is updated so that $s$ has the value determined by evaluating $e$ in the context of the thread's private variable valuation.  The thread's next statement is updated \PDComment{Do you mean execute?} according to the control flow graph of the current procedure.

@@

\medskip\noindent\textbf{Lockset instrumentation }
%
Suppose that $S$ and $T$ are thread templates for a concurrent program, including the possibly that $S=T$.
We wish to check whether it is possible for a thread that is an instance of $S$ to race with a thread that is
an instance of $T$, in the presence of arbitrarily many further threads.
